---
title: "STAT433 HW3"
author: "Lexi Luo"
date: "10/5/2021"
output: github_document
---

### Week4 HW3
https://github.com/QLexiLuo/STAT433-HW3


##### In r4ds flights… What time of day should you fly if you want to avoid delays as much as possible? Does this choice depend on anything? Season? Weather? Airport? Airline? Find three patterns (“null results” are ok!). Write your results into Rmarkdown. Include a short introduction that summarizes the three results. Then, have a section for each finding. Support each finding with data summaries and visualizations. Include your code when necessary. This shouldn’t be long, but it might take some time to find the things you want to talk about and lay them out in an orderly way.

```{r}
library(nycflights13)
library(dplyr)
library(ggplot2)
```

#### Summary
###### Leave in the morning, fly Alaska Airlines Inc., and fly from JFK airport may avoid delays as much as possible.

#### time of day
```{r}
avgdelay = flights %>%
  group_by(hour) %>%
  summarise(n = n(), arr_delay = mean(arr_delay, na.rm = TRUE)) %>%
  arrange(arr_delay) 

ggplot(data = avgdelay, aes(x= hour, y = arr_delay)) + 
  geom_bar(stat="identity", fill="grey") + 
  ylab('Average delay time per hour of the day (minutes)') +
  xlab('Hour') +
  theme_minimal() +
  scale_x_discrete(limits=avgdelay$hour)
```

This graph shows Hour vs. Average delay time per hour of the day, which demonstrated that morning flights before 10 am all have a negative delay time. 7 am flights had a lowest average delay time, which means people should take the 7 am flights if they want to avoid delays as much as possible.




#### Departure Airport
```{r}
delay_airport= flights %>%
  group_by(origin) %>%
  summarise(n = n(), arr_delay = mean(arr_delay, na.rm = TRUE)) %>%
  arrange(arr_delay) 

ggplot(data = delay_airport, aes(x= origin, y = arr_delay)) + 
  geom_bar(stat="identity", fill="light blue", width = 0.5) + 
  ylab('Average delay time (minutes)') +
  xlab('Departure Airport') +
  theme_minimal() +
  scale_x_discrete(limits=delay_airport$origin) +
  geom_text(aes(label=round(arr_delay,2)), vjust=1.6, color="black", size=3.5)
```

This graph shows Departure Airport vs. Average delay time for each airport, which demonstrated that JFK airport have the lowest average delay time in minutes, so people should fly from JFK if they want to avoid delays as much as possible.



#### Airline Carrier
```{r}
delay_carrier= flights %>%
  group_by(carrier) %>%
  summarise(n = n(), arr_delay = mean(arr_delay, na.rm = TRUE)) %>%
  arrange(arr_delay) 

ggplot(data = delay_carrier, aes(x= carrier, y = arr_delay)) + 
  geom_bar(stat="identity", fill="steelblue", width = 0.5) + 
  ylab('Average delay time (minutes)') +
  xlab('Airline Carrier') +
  theme_minimal() +
  scale_x_discrete(limits=delay_airport$carrier) +
  geom_text(aes(label=round(arr_delay,2)), vjust=1.6, color="black", size=3.5)
```

This graph shows Airline Carrier vs. Average delay time for each carrier, which demonstrated that Alaska Airlines Inc. has the lowest average delay time in minutes, so people should fly Alaska Airlines if they want to avoid delays as much as possible. 
